Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-04-01 GWLDCII.tex
second intro attempted

***Some general intro to WLDs.  It can probably gloss over most of what is already in the other paper, but this time we are going to talk about the denominator, so for context we should probably say something about the integral, and its poles in this intro.  Possibly also more about the integral should go at the end of the background section.***

In \cite{wilsonloop}, Agarwala and Amat show that Wilson loop diagrams can be interpreted as positroids, a certain well behaved class of realizable matroids.  This opens up the study of Wilson loop diagrams to techniques from geometry and combinatorics. 
In the companion paper to this one ***cite it*** we looked at equivalence classes of diagrams using matroidal and polytopal tools.  However, the combinatorial richness of positroids comes from more than just their matroidal nature, but from their many bijections with other interesting combinatorial structures, including plabic graphs, decorated permutations, and Le diagrams, see for instance \cite{Oh2}.

In this paper we will focus on implications of the Le diagrams on the mathematics and physics of Wilson loop diagrams.

>>>>

This paper is the second in a two part series investigating the combinatorics and geometry underlying SYM $N=4$ theory. This series lays out several results about the relationship between the Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian. This paper is concerned with identifying which positroid cells correspond to which Wilson loop diagrams, and how this translates to a geometric tiling of a subspace of the positive Grassmannians. Wilson loop diagrams associate a volume form to a positroid cell. In this paper, we give an algorithm to identify which cell corresponds to which diagram, via Grassmann Necklaces. Using the Le diagram representation of positroid cells, we prove results about the dimensions of these cells. Finally, we state some results about the structures of the volume forms defined on these positroid cells by the Wilson loop diagrams.

In contrast, the first paper in this series is about combinatorial and matroidal properties of the Wilson loop diagrams. The main focus of that paper was to enumerate the positroid cells that appeared in the image of the association between diagrams and cells, as well as the size of the number of Wilson loop diagrams in the pre-image of any positroid cell under this association.s is given by counting the directions of associahedrons.

In recent years, there has been a some interest in understanding the geometry and combinatorics underlying the field theory SYM $N=4$ \cite{wilsonloops, amplituhedron, correlahedron, karpwilliams, galashinlam}. This started with the observation BCFW diagrams, which represent the on shell interactions of this theory correspond to plabic graphs \cite{bigamplituhedronpaper.} Plabic graphs are one of the many equivalent ways to identify positroid cells of the positie Grassmannians \cite{Postnikov}. This work led to the representation of the on shell integrals associated this theory in terms of a geometric space embedded in $\Gr(k,n)$, called the Amplituhedron \cite{amplituhedron, amplituhedron2}. More over, inegrals associated to the BCFW diagrams define a volume form on the Amplituhedron Since then, there has been significant work to understand the volume form and its physical implications \cite{galashinlam, others}.

Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{BullimoreSkinner, AldayMaldecena?, Wittenpaper}. These integrals are calculated via holomorphic Wilson loops. As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams. The sum of the corresponding sum of Feynman integrals associate a volume form to space \cite{Hodges?}. The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloops}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, correlahedron}.

In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron. They are not the same. For in stance, \cite{non-orientable} shows that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$, while it is conjectured that the Amplituhedron is orientable. Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, as one sees from counting arguments in comparing the results of \cite{KarpWiliams} and \cite{casestudy}. This is not too alarming, as one expects space parametrized by the Wilson loop diagrams to project down to something close to the Amplituhedron \cite{wilsonloops, correlahedron}.

This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram. Where the BCFW diagrams identify positroid cells via plabic graphs, in this paper, we give an algorithm to read off of a Wilson loop diagram the associated Grassmann Necklace. Furthermore, while the BCFW cells are all 4k dimensional, we show that the positroid cells associated to Wilson loop diagrams are $3k$ dimensional. Again, this is not alarming, as \cite{non-orientable} has shown that the actual geometric space parametrized by the Wilson loop diagrams is a non-orientable $k$ dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.

Finally, when computing a finite volume to a geometric object defined by the Wilson loop diagrams, one must ensure at any singularities cancel. This has been expicitly shown in a few cases \cite{casestudy, HeslopStewart}, but it has been hard to prove exactly due to the non-one to one or onto relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$. In this paper, we give a characterisation of the denominator of the Feynman integral defined by a Wilson loop diagram in terms of the algorithm that associated the same diagram to a Grassman Necklace.
